Sparse Function-space Representation \\ of Neural Networks

### 2023-05-13 paper/main.tex
written some dual variable stuff

\textbf{Sparse Dual Gaussian Process} Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low rank approximation many approaches have been devised see \citet{quinonero2005unifying} for an overview. Given we have our dual variables derived from our neural network predictions and kernel function we could make use any approximation. We decide to follow the the \citep{titsias2009variational}, which is to say that our marginal distribution $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$

>>>>

\textbf{Sparse Dual Gaussian Process} Sparse Gaussian processes are a way to reduce the computational complexity of a full GP using a low-rank approximation. Many sparsifying approaches exist (see \citet{quinonero2005unifying}) for an overview. Given that we have our dual variables derived from our neural network predictions and kernel function, we could use any approximation. We decide to follow the sparsifying approach of \citep{titsias2009variational}, which is to define the marginal distribution as $q_{\vu}(f_i)  = \int p(f_i  \mid \vu) q(\vu)  d\vu$. Given that we have $p(f_i  \mid \vu)$ determined by our GP prior, the goal is to find a $q(\vu)$. As was shown in \cite{adam2021dual}, the posterior under this model has a particular structure similar to \cref{eq:gp_pred}. In that paper, they spot the dual variables' importance for approximate inference but write them in the natural parameter form as this form is more suitable for optimization through natural gradients. In order to make the link
